An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-05 Article/EconGrowth2.Rnw
EconGrowth2.Rnw now uses AllCoef.rda dna AllFitted.rda. Using %in% for all filtering.

# Load coefficients from all models in one large data frame
coef_df<- tbl_df( readRDS("../AllCoef.rda") )
fitted_df <- tbl_df( readRDS("../AllFitted.rda") )

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
# archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.

# Load the original models.
# f <- gzcon(unz(description=archive, filename=file.path("../oModels.Rdata")))
oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
close(f)

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
cdCoeffsData <- filter(coef_df, model=="cd", nestStr==c("iK+iL", "iK+iL+iQ"))

# Rearrange the country factors to obtain our preferred ordering.
cdCoeffsData$country <- as.factor(cdCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cdCoeffsData$country <- relevel(cdCoeffsData$country, ref=lev) }
# Rearrange the energy factors to obtain our preferred ordering.
cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(is.na(cdCoeffsData$energy)), "none")
cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(cdCoeffsData$energy=="iQ"), "q")
cdCoeffsData$energy <- as.factor(cdCoeffsData$energy)
energyLevels <- c(none="none", q="q")
for (lev in rev(energyLevels)) { cdCoeffsData$energy <- relevel(cdCoeffsData$energy, ref=lev) }
standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData <- filter(fitted_df, model=="cd", nest==c("iK+iL", "iK+iL+iQ"))
# Rearrange the energy factors to obtain our preferred ordering.
cdFittedData$energy <- replace(cdFittedData$energy, which(is.na(cdFittedData$energy)), "none")
cdFittedData$energy <- replace(cdFittedData$energy, which(cdFittedData$energy=="iQ"), "q")
cdFittedData$energy <- as.factor(cdFittedData$energy)
energyLevels <- c(none="none", q="q")
for (lev in rev(energyLevels)) { cdFittedData$energy <- relevel(cdFittedData$energy, ref=lev) }
spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesCoeffsData <- filter(coef_df, model=="ces", nestStr==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
# Rearrange the country factors to obtain our preferred ordering.
cesCoeffsData$country <- as.factor(cesCoeffsData$country)
for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
# cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
# standardTriPlot(data=cesTriPlotData)
standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
cesFittedData <- filter(fitted_df, model=="ces", nest==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- loadResampledData(archive=archive, 
                                     country=countryAbbrevs, 
                                     model="linex", 
                                     factors=c("iK+iL+iQ"), 
                                     kind="coeffs")
# Rearrange the country factors to obtain our preferred ordering.
linexCoeffsData$country <- as.factor(linexCoeffsData$country)
for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }

standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- loadResampledData(archive=archive, 
                                     country=countryAbbrevs, 
                                     model="linex",
                                     factors=c("iK+iL+iQ"), 
                                     kind="fitted")

spaghettiPlot(data=linexFittedData, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

>>>>

# Load coefficients from all models in one large data frame
coef_df <- tbl_df( readRDS("../AllCoef.rda") )
# Rearrange the country factors to obtain our preferred ordering.
coef_df$country <- as.factor(coef_df$country)
for (lev in rev(countryAbbrevs)) { coef_df$country <- relevel(coef_df$country, ref=lev) }
# Change the names of the energy factors to the names for the graph
coef_df$energy <- replace(coef_df$energy, which(is.na(coef_df$energy)), "none")
coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iQ"), "q")
coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iX"), "x")
coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iU"), "u")
# Rearrange the energy factors to obtain our preferred ordering.
coef_df$energy <- as.factor(coef_df$energy)
energyLevels <- c(none="none", q="q", x="x", u="u")
for (lev in rev(energyLevels)) { coef_df$energy <- relevel(coef_df$energy, ref=lev) }

# Load fitted data from all models in one large data frame
fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
# Rearrange the energy factors to obtain our preferred ordering.
fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
fitted_df$energy <- as.factor(fitted_df$energy)
for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }

# Load the original models.
oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
close(f)

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
cdCoeffsData <- filter(coef_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesCoeffsData <- filter(coef_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- filter(coef_df, model=="linex", energy=="q")
standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}
